%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Software Development \& QA Combo Co-op} % Job title
    {ECFMG (Educational Commission for Foreign Medical Graduates)} % Organization
    {Remote} % Location
    {Mar. 2020 - Sept. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Built and maintained Windows applications using C\# and VB (Visual Basic)
        \item Maintained web pages via ASP.Net, HTML, and JavaScript
        \item Performed QA tasks such as migration testing, system testing, load testing, etc.
        \item Documented reoccurring company processes in an effort aid knowledge transfers and overall wiki documentation
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Op Applications Engineer} % Job title
    {Oracle Corporation} % Organization
    {Conshohoken, Pennsylvania} % Location
    {Sept. 2018 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Supported a cloud-integrated business management software utilizing Agile Methodologies (Oracle Prime)
        \item Client side web application development in JavaScript, back end server development in Java
        \item Test driven development using unit testing frameworks such as JUnit, Mockito, and Selenium
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer Co-Op / Part-Time} % Job title
    {Susquehanna International Group, LLP} % Organization
    {Bala Cynwyd, Pennsylvania} % Location
    {Sept. 2017 - Sept. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed internal Windows applications and web apps that supports developers and traders using C\# and ASP.NET
        \item Utilized REST API's and SMTP Mail Clients to alert developers on merge requests and related JIRA issues (JSDWebhook)
        \item Built a network crawler to check DLL version numbers for product releases and web apps (SFG Owl)
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant \& STAR Scholar} % Job title
    {Drexel University Office of Undergraduate Research} % Organization
    {Philadelphia, Pennsylvania} % Location
    {Dec. 2016 - Sept. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Wrote applications for Biomedical Informatics research testing the efficacy of a Facebook smoking cessation intervention
        \item Used the Facebook API to extract group data and format/save the data into JSON files using Java
        \item Visualized the information into interactive charts using D3.js, HTML, and JavaScript
        % \item Started off as a research assistant for Dr. Christopher Yang, later applied to the STAR (Students Tackling Advanced Research) Scholars program to continue researching over the summer
        \item Presented the application and research findings at the STAR Scholars gala at the end of the program
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
